Termination and Non-Termination Proofs for Bit-Vector Programs

### 2014-10-17 papers/termination/termination-esop/paper.tex
fixed the motivational examples figure
change title+keywords

\title{Synthesising Termination and Non-Termination Proofs for Bit-Vector Programs}

@@

\keywords
Termination, Non-Termination, Program Synthesis,
Lexicographic Ranking Functions, Bit-vector Ranking Functions, Floating-Point Ranking Functions.

@@

\begin{figure*}
\footnotesize{
\centering
\begin{tabular}{ccc}
\begin{subfigure}[b]{0.3\textwidth}
\small{
\begin{lstlisting}
while (x > 0) {
  x = (x - 1) & x;
}
\end{lstlisting}
\caption{Taken from~\cite{DBLP:conf/tacas/CookKRW10}.}
 \label{fig:motivation.a}
}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x != 0) {
  x = -x / 2;
}
\end{lstlisting}
\caption{}
 \label{fig:motivation.b}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}[language=C]
while(x > 0) {
  x++;
}
 \end{lstlisting}
\caption{}
 \label{fig:motivation.c}
\end{subfigure} \\

@@

\begin{subfigure}[b]{0.3\textwidth}

\begin{lstlisting}
while (i < M || j < N) {
  i = i + 1;
  j = j + 1;
}
\end{lstlisting}
\caption{Taken from~\cite{DBLP:conf/sigsoft/Nori013}}
 \label{fig:motivation.d}
\end{subfigure}

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
float x;

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x != 0) {
  if (x > 0)
    x--;
  else
    x++;
}
\end{lstlisting}
\caption{Taken from \cite{DBLP:conf/tacas/CookSZ13}}
 \label{fig:motivation.g}
\end{subfigure}

@@

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
y = 1;

while (x > 0) {
  x = x - y;
}
\end{lstlisting}
\caption{}
 \label{fig:motivation.h}
\end{subfigure}

\begin{subfigure}[b]{0.3\textwidth}
\begin{lstlisting}
while (x>0 && y>0 && z>0) {
  if (y > x) {
    y = z;
    x = nondet();
    z = x - 1;
  } else {
    z = z - 1;
    x = nondet();
    y = x - 1;
  }
}
\end{lstlisting}
\caption{Taken from~\cite{BA:mcs}}
 \label{fig:motivation.i}
\end{subfigure} 
% 
% \\
% 
% \hline
% 
% &
% 
% \begin{subfigure}[b]{0.3\textwidth}
% \begin{lstlisting}
% while (i < n) {
%   j = 0;
%   while (j <= i) {
%     j = j + 1;
%   }
%   i = i + 1;
% }
% \end{lstlisting}
% \caption{Taken from~\cite{DBLP:conf/cav/BrockschmidtCF13}}
% \end{subfigure}
\end{tabular}
}
\caption{Motivational examples, mostly taken from the literature.\label{fig:motivation}}
\end{figure*}

>>>>

\title{Termination and Non-Termination Proofs for Bit-Vector Programs}

@@

\keywords
Termination, Non-Termination, 
Lexicographic Ranking Functions, Bit-vector Ranking Functions, Floating-Point Ranking Functions.

@@

\begin{figure*}[h]
\hspace*{-2.5cm}
\centering
%\resizebox{.95\textwidth}{!}{
%\begin{minipage}{\linewidth}
\begin{tabular}{ccc}
\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
while (x > 0) {
  x = (x - 1) & x;
}
\end{lstlisting}
\caption{Taken from~\cite{DBLP:conf/tacas/CookKRW10}.}
 \label{fig:motivation.a}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
while (x != 0) {
  x = -x / 2;
}
\end{lstlisting}
\caption{}
 \label{fig:motivation.b}
\end{subfigure}%

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}[language=C]
while(x > 0) {
  x++;
}
 \end{lstlisting}
\caption{}
 \label{fig:motivation.c}
\end{subfigure} \\

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
while (i<M || j<N) {
  i = i + 1;
  j = j + 1;
}
\end{lstlisting}
\caption{Taken from~\cite{DBLP:conf/sigsoft/Nori013}}
 \label{fig:motivation.d}
\end{subfigure}

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
float x;

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
while (x != 0) {
  if (x > 0)
    x--;
  else
    x++;
}
\end{lstlisting}
\caption{Taken from \cite{DBLP:conf/tacas/CookSZ13}}
 \label{fig:motivation.g}
\end{subfigure}

@@

\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
y = 1;

while (x > 0) {
  x = x - y;
}
\end{lstlisting}
\caption{}
 \label{fig:motivation.h}
\end{subfigure} 
&
\begin{subfigure}[b]{0.45\textwidth}
\begin{lstlisting}
while (x>0 && y>0 && z>0){
  if (y > x) {
    y = z;
    x = nondet();
    z = x - 1;
  } else {
    z = z - 1;
    x = nondet();
    y = x - 1;
  }
}
\end{lstlisting}
\caption{Taken from~\cite{BA:mcs}}
 \label{fig:motivation.i}
\end{subfigure} 
\end{tabular}
%}
\caption{Motivational examples, mostly taken from the literature.\label{fig:motivation}}
\end{figure*}
